---
title: 'Report Assessment Ch5 Subsidies Reform'
subtitle: 'Data Management Report'
author:
  - name: Rainer M Krug
    id: rmk
    orcid: 0000-0002-7490-0066
    email: Rainer.Krug@Senckenberg.de, Rainer@Krugs.de
    affiliation: 
      - name: Senckenberg
        city: Frankfurt (Main)
        url: https://www.senckenberg.de/en/institutes/sbik-f/
    roles: [author, editor]
abstract: > 
  A short description what this is about.
  This is not a tracditional abstract, but rather something else ...
# keywords:
#   - aaaaa
#   - bbbbb
license: "CC BY"
copyright: 
  holder: No idea
  year: 2023
citation: 
  type: report
  container-title: IPBES Data Management Report
  doi: XXXXXX
doi: XXXXXX
version: 0.0.1

format:
    html:
        toc: true
        toc-depth: 4
        toc_expand: true
        embed-resources: true
        code-fold: true
        code-summary: 'Show the code'

---

```{r}
#| label: setup
#| include: false

if (!exists("params")) {
    params <- rmarkdown::yaml_front_matter("Report.qmd")$params
}


build <- as.integer(readLines("buildNo"))
build <- build + 1
writeLines(as.character(build), "buildNo")

knitr::opts_chunk$set(message = NA)

library(openalexR)

compact <- function(x) {
    x |>
        gsub(pattern = "\n", replacement = " ") |>
        gsub(pattern = "\\*", replacement = "") |>
        gsub(pattern = "\\s+", replacement = " ") |>
        gsub(pattern = "\\( ", replacement = "(") |>
        gsub(pattern = " )", replacement = ")")
}

R1_st <- list()

st <- readLines(file.path("input", "R1.txt"))[1:70]
st[70] <- gsub(pattern = " OR", replacement = "", st[70])
R1_st[[1]] <- paste(collapse = " ", st)

st <- readLines(file.path("input", "R1.txt"))
st <- st[71:length(st)]
R1_st[[2]] <- paste(collapse = " ", st)

rm(st)

R2_st <- readLines(file.path("input", "R2.txt")) |>
    paste(collapse = " ")

```

## Working Title
IPBES_TCA_Ch5_Subsidies_Reform

## Code repo

[Github - private](https://github.com/IPBES-Data/IPBES_TCA_Ch5_Subsidies_Reform)

## Build No: `r build`

%The BuidNo is automatically increased by one each time the report is rendered. It is used to indicate different renderings when the version stays the same%.

## Introduction

### The following steps will be done in documented in this report:

- [x] Do asearch with `R1_st` and `R2_st` and determine the  number of hits
- [ ] Should the copplete `**R1** AND **R2**` be downloaded, or only a random subsets?


## Step 1: Determination of numbers

The search terms are based on the [shared google doc](https://docs.google.com/document/d/1_FmxYVhpv2Bu2Gbbxb7cWc49f3soFvc64Qau_x2RAqI){target=_blank}. They are cleaned up for the usage in [OpenAlex](https://openalex.org/){target=_blank}.

## R1

The search terms is [R1](input/R1.txt){target=_blank}

```{r}
#| label: get get_R1_count
#|

R1_count <- sapply(
    R1_st,
    function(st) {
        openalexR::oa_fetch(
            title_and_abstract.search = compact(st),
            count_only = TRUE,
            verbose = TRUE
        )[, "count"]
    }
) |>
    sum()
```


## R2

The search terms is [R2](input/R2.txt){target=_blank}

```{r}
#| label: get get_R2_count
#|

R2_count <- openalexR::oa_fetch(
    title_and_abstract.search = compact(R2_st),
    count_only = TRUE,
    verbose = TRUE
)[, "count"]
```

## R1 AND R2

The search term is [R1](input/R1.txt){target=_blank} AND [R2](input/R2.txt){target=_blank}

```{r}
#| label: get get_R2_R2_count
#|

R1_R2_count <- sapply(
    R1_st,
    function(st) {
        openalexR::oa_fetch(
            title_and_abstract.search = compact(paste0("(", st, ") AND (", R2_st, ")")),
            count_only = TRUE,
            verbose = TRUE
        )[, "count"]
    }
) |>
    sum()

```

## Results

### Number of hits
- **R1:**: `r formatC(R1_count, format="f", big.mark=",", digits=0)` hits
- **R2:** `r formatC(R2_count, format="f", big.mark=",", digits=0)` hits
- **R1 AND R2:** `r formatC(R1_R2_count, format="f", big.mark=",", digits=0)` hits

These are numbers which can easily be downloaded, either as a single set or several random sets.